A Recurrence

### 2014-11-24 draft.tex
started second section

\documentclass[12pt]{article}
\usepackage{amsmath}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{proposition}{Proposition}

@@

\section{The case of $F(x,y) = f(y)/x$}

We begin by studying the special case where $F(x,y) = \dfrac{f(y)}{x}$. So that means that the sequences are defined by the relation
\begin{equation}
\label{eq:firstcase}
a_{n+1} = \dfrac{f(a_{n-1})}{a_n}
\end{equation}
In the introduction, we've already seen two functions in this form that are periodic. Namely, $f(y) = 1$ and $f(y) = \frac{1}{y}$.

\begin{proposition}
The only possible $f$ which yields a sequence of period $3$ according to the recurrence in Equation~\ref{eq:firstcase} is $f(y) = \dfrac{c}{xy}$.
\end{proposition}

\begin{proof}
We can look at the first few values of the sequence:
\[ x, y, \dfrac{f(y)}{x}, x, y, \dots \]
By looking at $a_4$, observe that
\[ y = \dfrac{xf(x)}{f(y)} \]
and so,
\[ y f(y) = x f(x) \]
Fix $x = 1$. Then we have $y f(y) = f(1)$, and so $f(y) = \dfrac{c}{y}$, where $c$ is any constant .
\end{proof}

Likewise, we can do a similar analysis for period $4$. 
\begin{proposition}
The only possible $f$ (polynomial) which yields a sequence of period 4 according to the recurrence in Equation~\ref{eq:firstcase} is $f(y) = c$. 
\end{proposition}

\begin{proof}
First, we can easily check that these functions yield a sequence with period $4$. If we had any function $f$ which yielded a sequence with period $4$, then 
\[ x, y, \dfrac{f(y)}{x}, \dfrac{f(f(y)/x)}{y}, x, y, \dots \]
And by looking at $a_6$, observe
\[ y = \dfrac{yf(x)}{f(f(y)/x)} \]
and so 
\[ f(f(y)/x) = f(x) \]
If we fix $x = 1$, then we have
\[ f(f(y)) = f(1) \]
Which means that $f(f(y))$ is a constant for every $y$. And so since $f(y)$ is non-constant, it will take on infinitely many values, which means that $f(y) - f(1)$ is also a polynomial with infinitely many roots, and so $f(y) = f(1)$. 
\end{proof}
